### 2020-02-11 ChapterResults/chapterResults.tex
Added: Ratio graphs for results

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances unless otherwise stated: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. An experiment was carried out for each aura tolerance, for each experiment, three tolerances values were chosen. The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen.

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $64m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedHigh}
\end{figure}
	%\label{fig_CollisionsPenVsSpeed}
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

@@

>>>>

\subsubsection{Experiment parameters and output}
The two servers use the following tolerances unless otherwise stated: a maximum speed tolerance of $32m\mathord{\cdot}s^{-1}$; maximum latency tolerance of $2ms$; and a maximum frame-time tolerance of $15ms$. Each server has a random delay before starting between $0$ and the target frame-time in order to prevent the two servers always having synchronous update cycles. Each experiment is repeated $50$ times. An experiment was carried out for each aura tolerance value, for each experiment, three tolerances values were chosen. For each tolerance value, the following graphs were plotted:
\begin{itemize}
	\item The ratio of late to correct collisions and ratio of misses to total collision.
	\item The mean and $+/-2$ standard deviations of penetration time were plotted against each tolerance factor for each of the three tolerance values chosen.
\end{itemize}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsSpeedHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a speed tolerance of $48m\mathord{\cdot}s^{-1}$. The speed tolerance is marked in a dashed green line.}
	\label{fig_RatioVsSpeedHigh}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedLow}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $16m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedMid}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $32m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{MeanPenVsSpeedHigh}
	\caption{Mean penetration time of objects with $+/-2$ standard deviations with varying speed using a speed tolerance of $48m\mathord{\cdot}s^{-1}$. The maximum expected penetration time of 1 physics step is marked with a dashed blue line. The speed tolerance is marked in a dashed green line.}
	\label{fig_CollisionsPenVsSpeedHigh}
\end{figure}
	%\label{fig_CollisionsPenVsSpeed}
%\begin{figure}
%	\centering
%	\includegraphics[width=\textwidth]{CollisionsPenVsSpeed}
%	\caption{Penetration time of objects with varying relative speed. Each red point represents one or more collisions. The maximum expected penetration time of 1 physics steps is marked with a dashed blue line. The speed tolerance is marked in a dashed green line. The number and magnitude of errors increases as relative speed increases beyond the tolerance.}
%	\label{fig_CollisionsPenVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{MeanMaxErrorVsSpeed}
%\caption{The mean and max of collision errors with varying relative speed}
%\label{fig_MeanMaxErrorVsSpeed}
%\end{figure}
%
%\begin{figure}
%\centering
%\includegraphics[width=\textwidth]{RatiosVsSpeed}
%\caption{The ratios of erroneous collisions to correct collisions and missed collisions to total collisions with varying relative speed}
%\label{fig_RatiosVsSpeed}
%\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a latency tolerance of $2ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a latency tolerance of $8ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsLatencyHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. Speed using a latency tolerance of $16ms$. The latency tolerance is marked in a dashed green line.}
	\label{fig_RatioVsLatencyHigh}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeLow}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs. frame-time using a frame-time tolerance of $8ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeLow}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeMid}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs.frame-time using a frame-time tolerance of $15ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeMid}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=\textwidth]{RatiosVsFrameTimeHigh}
	\caption{Ratio of Late to Correct Collisions and Misses to Total Collision vs.frame-time using a frame-time tolerance of $25ms$. The frame-time tolerance is marked in a dashed green line.}
	\label{fig_RatioVsFrameTimeHigh}
\end{figure}
